\documentclass[a4paper]{article}
\usepackage[spanish,english]{babel}
% \usepackage[spanish]{babel}
\usepackage{t1enc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
% \usepackage{t1enc}
% \usepackage{fullpage}
\usepackage{a4wide}
\usepackage{graphicx}
\usepackage{wrapfig}
% \usepackage{float}

\usepackage{fancyhdr}
\fancyhead[L]{\Large
Gastón A. Avila, PhD.
% 27 de Abril 1935, 2 I \\
% X5002AAG Córdoba, Argentina  \\
% e-mail: \tt{avila.gas@gmail.com} \\
% Tel: +54 9 351 2 055 880
}
\fancyhead[R]{\Large Curriculum Vitae}
\renewcommand{\headrulewidth}{1pt}

\pagestyle{plain}

\newcommand{\HRule}{\noindent\rule{\linewidth}{1pt}}

\title{CURRICULUM VITAE}
\date{\today}
\author{Gastón Alejandro Avila}

\begin{document}
\maketitle

\subsection*{Personal Information:}

\begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}} l p{0.6\textwidth} }
% \textbf{Name:} & Gastón Alejandro Avila\\
\textbf{Date of Birth:} & 16th of august 1982\\
\textbf{Place of Birth:} & Córdoba Capital, Córdoba, Argentina\\
\textbf{Nacionalities:} & Argentine, Italian\\
\textbf{Work address:} &
Max-Planck Institute for Gravitational Physics

Am Mühlenberg 1,
D-14476 Potsdam, Germany\\
\textbf{Private address:} & Alt-Moabit 74B, D-10555 Berlin, Germany\\
\textbf{Phone Number:} & +49 176 8307 8417\\
\textbf{E-mail:} & \texttt{gavila@aei.mpg.de}
\end{tabular*}

\noindent\hrulefill

\section{Education}
\begin{itemize}
\item \textbf{Graduate School:} (Since 05/2008) PhD. Student, Potsdam
University, Germany. Adviser: Prof. Helmut Friedrich. Supported by and carried
out at:
Max Planck Institute for Gravitational Physics (Albert Einstein Institute)
% Position Start: 04/05/2008  
% Position End: 19/10/2011

 \item \textbf{University:} (2002 - 2008) Licenciatura en Física, FaMAF,
Universidad Nacional de Córdoba, Argentina. Average grade obtained 9.57 out of
10.
%Graduated on the 27/03/2008

 \item \textbf{High School:} (1996 - 2001) Bachiller Técnico Metal-Meácnico
especialista en Máquinas Herramienta, Instituto Técnico Renault, Córdoba,
Argentina. % Graduated with the highest average grade of the class of 2011.
\end{itemize}

\section{Teaching Experience}
\begin{itemize}
 \item(03/2010--09/2010) Teaching Assistant: Classical Mechanics. Potsdam
University, Germany.
% DATES???
 \item(03/2007--03/2008) Teaching Assistant (Type A). FaMAF, UNC, Argentina.
 \item(03/2005--03/2007) Teaching Assistant (Type B). FaMAF, UNC, Argentina.
%  \item[01/2006--06/2007] Tutor and Supervisor, Online Tutor on College and
% Pre-college Matematics in English, Latinhire, Chile. (subcontracted Tutor.com)
\end{itemize}

\section{Informatics skills}
\begin{itemize}
 \item OSs: Linux (Ubuntu), Mac OS X
 \item Languages: Python, JavaScript, SQL, Html5
 \item GIS y geolocation: OpenStreetMap, JOSM, Merkaartor, Maperitive, Mapnik
 \item Client side Web frameworks: Backbone.js, Angular.js, Openlayers.js, Google Maps API 
v3
 \item Server side Web: WSGI Python (Flask, Bottle), Node.js (Express.js), 
RESTful APIs using SWAGGER,
 \item Databases: PostgreSQL, SQLite, mongoDB,
\end{itemize}

\section{Work experience}
\begin{itemize}
 \item (08/2014 -- now) Sistemas Globales S. A., web UI analyst Senior. 
Tech Lead in hybrid proyect using angularjs + cordova for iPhone. Client: Virgin Mega
 \item (04/2014 -- now) Ministerio de Transporte de la Provincia de Mendoza, 
 technical advisor in applications to public transit. Web apps for geo-location, data analysis and modeling.
 \item (04/2013 -- 08/2014) Sistemas Globales S. A., web UI analyst. 
Tech Lead in node.js + Backbone.js. Client: Thomas Cook
 \item (12/2011 -- 06/2014) Municipalidad de Córdoba, technical advisor in applications to public transit.
 Comisión de Movilidad Integral. Web apps for geo-location, data analysis and modeling.
 \item (04/2008 -- 11/2011) Max Planck Institute for Gravitational Physics
(Albert Einstein Institute)
\end{itemize}

\section{Languages}
\begin{itemize}
 \item \textbf{Spanish:} Native.
 \item \textbf{English:} Reads, writes and speaks
\end{itemize}

\section{Publications}
\begin{enumerate}
\item \newblock \emph{Asymptotic staticity and tensor decompositions with fast
decay conditions}
\newblock (Doctoral disertation)
\newblock Gast\'{o}n~A Avila, PhD.
\newblock {Institutional Repository of the University of Potsdam},
\url{http://opus.kobv.de/ubp/volltexte/2011/5404/} 07.10.2011.

\item \newblock \emph{The Yamabe invariant for axially symmetric initial data of
two Kerr black holes.}
\newblock Gast\'{o}n~A Avila and Sergio Dain.
\newblock { Classical and Quantum Gravity}, 25(22):225002 (13pp), 2008.
\end{enumerate}

\section{Talks}
\begin{itemize}
 \item \emph{Tensor decompositions with fast decay conditions at space-like
infinity}, Grav11 - FaMAF, Córdoba, Argentina. 11/04/2011.
 \item \emph{Tensor decompositions with fast decay conditions at space-like
infinity}, Workshop on Mathematical Relativity - ESI, Vienna, Austria.
28/01/2011.
 \item \emph{The Yamabe invariant for axially symmetric two Kerr black
holes initial data}, Grav09 - Córdoba Argentina. 15/04/2009.
\end{itemize}

\section{Scientific Meetings}
\begin{itemize}
 \item \emph{Grav11}, Congress on General Relativity and Gravitation (FaMAF),
La Cumbre, Córdoba, Argentina. 11/04/2011 - 15/04/2009. 
 \item \emph{Workshop on Mathematical Relativity}, International Centre for
Mathematical Science - Edinburgh, UK. 1/09/2009 - 7/09/2010.
 \item \emph{Seminar on Mathematical Relativity} - Erwin Schroedinger
Institute, Vienna, Austria. 27/01/2011 - 29/01/2011.
 \item \emph{Space, Time and Beyond}. Conference in honor of Helmut
Friedrich's birthday.
08/10/2009 - 09/10/2009.
 \item \emph{Grav09}, Congress on General Relativity and Gravitation, FaMAF,
Córdoba, Argentina. 13/04/2009 - 17/04/2009. 
 \item \emph{Grav07}, Congress on General Relativity and Gravitation, FaMAF,
Córdoba, Argentina. 5/11/2007 - 7/11/2007. %Asistent
 \item \emph{Grav06}, Fifty years of FaMAF \& Workshop on Global Problems in GR,
FaMAF, Córdoba, Argentina. 6/10/2006 - 11/10/2006. %Asistent
\end{itemize}

\section{Honors}
\begin{itemize}
 \item Graduated Top of the class 2001 - Instituto Técnico Renault,%(High
% School)
 \item Awarded Academic Excellence Price 2001, by Banco Roela, Argentina.
% (Premio a la exelencia académica, Banco Roela)
\end{itemize}


\vspace{3\baselineskip}

\begin{flushright}
\rule{7cm}{0.2mm}

%  Berlin,
 \today
\end{flushright}


\end{document}
